### 2025-05-22 paper-reviews/papers-2025.tex
Add SpeedRacer attack paper

>>>>

\section*{Software Attacks}

\begin{itemize}
    \item \cite{Kallenberg:SpeedRacer:2014}:

    The paper demonstrates how race conditions in Intel flash protection mechanism can be used to overwrite UEFI firmware. The attack utilizes race condition between a malicious thread running supervisor mode and BIOS protection thread running in SMM. The software threads can run on different hyper threads. Even though Intel chipsets provide a mechanism to protect against the attacks, neither reference UEFI implementation not UEFI provided by OEMs use the protection mechanisms as of the state when the paper was written.
\end{itemize}
